---
title: "hw5"
author: "Yiyao LI"
date: "2020/11/14"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
set.seed(7)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in data

```{r}
homicide_df = 
  read_csv("./homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~"unsolved",
      disposition == "Open/No arrest" ~"unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
select(city_state, resolved) %>% 
  filter(city_state !="Tulsa_AL")
```


```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

do a prop test for a single city

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

try to iterate

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

write a function for prop test

```{r, error = TRUE}
city_prop_test = function(df) 



city_prop_test(Atlanta_GA)
```


## Problem 2


import one dataset 

```{r}
data_1 = read_csv("hw5_data/con_01.csv")
```

```{r, error = TRUE}
path_df = 
  tibble(
    path = list.files("hw5_data"),
  ) %>% 
  mutate(
    path = str_c("hw5_data/", path),
    map_df(.x = path, read_csv)) %>% 
  bind_cols()
```

tidy the data

```{r}
tidy_df =
path_df %>% 
mutate(
    path = str_replace(path, "hw5_data/", ""),
    path = str_replace(path, "\\.csv", "")) %>% 
  rename(arm = path) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value")
```

Make a spaghetti plot 

```{r}
tidy_df %>% 
  mutate(week = str_replace(week, "week_", "")) %>%
  ggplot(aes(x = week, y = value, group = arm, color = arm))+
  geom_line()
```
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups




## Problem 3

generate 5000 datasets 

write a function and simulate a lot

```{r}
sim_t_test = function(samp_size = 30, mu = 0, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(samp_size, mean = mu, sd = sigma),
  )
  
  sim_data  = t.test(sim_data) %>% 
  broom::tidy() %>% 
  select(estimate, p.value)
  
  sim_data
  
  
}
```

```{r}
sim_results = 
  tibble(mu_true = c(0,1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x = mu_true, ~rerun(5000, sim_t_test(mu = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)
```

times of the null was rejected

```{r}
plot_data_df = 
sim_results %>% 
    group_by(mu_true) %>% 
    filter(p.value<0.05) %>% 
    summarize(
      times = n(),
      times = times/5000
      )
  
plot_data_df %>% 
  ggplot(aes(x = mu_true, y = times))+
    geom_point()

```

Describe the association between effect size and power.




```{r}
plot2_data = 
sim_results %>% 
  group_by(mu_true) %>% 
  summarize(estimate_mu = mean(estimate))

plot2_data %>% 
ggplot(aes(x = mu_true, y = estimate_mu))+
  geom_line()
```

```{r}
plot3_data = 
  sim_results %>% 
    group_by(mu_true) %>% 
    filter(p.value<0.05) %>% 
    summarize(estimate_mu = mean(estimate))

plot3_data %>% 
ggplot(aes(x = mu_true, y = estimate_mu))+
  geom_line()
```

